Music Perception: Stimuli profiles

### 2021-02-21 material/expstimuli/stimuli.Rmd
remove irrelevant variable names
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

# packages
if (!require("ggpubr")) {install.packages("ggpubr"); require("ggpubr")}

@@

# KV

```{r vel, include = FALSE}
dt_vel <- data_onset
dt_vel$Note <- rep(1:72, nrow(dt_vel)/72)

# assign Subcomponents
# for each note
dt_vel$Subcomponent <- "NA"
# Legato
for (phrase in 1:length(ls_legato2)){
   for (note in 1:length(ls_legato2[[phrase]])){
     dt_vel[Skill == "articulation" & Note == ls_legato2[[phrase]][note]]$Subcomponent <- "Legato"
   }
}
# Staccato
for (phrase in 1:length(ls_staccato2)){
   for (note in 1:length(ls_staccato2[[phrase]])){
     dt_vel[Skill == "articulation" & Note == ls_staccato2[[phrase]][note]]$Subcomponent <- "Staccato"
   }
}

@@

# assign Subcomponents
# for intervals
dt_vel_diff$Subcomponent <- "NA"
# Legato
for (phrase in 1:length(ls_legato)){
for (note in 1:length(ls_legato[[phrase]])){
  dt_vel_diff$Subcomponent[dt_vel_diff$Skill == "articulation" & dt_vel_diff$Interval == ls_legato[[phrase]][note]] <- "Legato"
}
}
# Staccato
for (phrase in 1:length(ls_staccato)){
for (note in 1:length(ls_staccato[[phrase]])){
  dt_vel_diff$Subcomponent[dt_vel_diff$Skill == "articulation" & dt_vel_diff$Interval == ls_staccato[[phrase]][note]] <- "Staccato"
}
}

# Forte
for (phrase in 1:length(ls_forte)){
for (note in 1:length(ls_forte[[phrase]])){
  dt_vel_diff$Subcomponent[dt_vel_diff$Skill == "dynamics" & dt_vel_diff$Interval == ls_forte[[phrase]][note]] <- "Forte"
}
}
# Piano
for (phrase in 1:length(ls_piano)){
for (note in 1:length(ls_piano[[phrase]])){
  dt_vel_diff$Subcomponent[dt_vel_diff$Skill == "dynamics" & dt_vel_diff$Interval == ls_piano[[phrase]][note]] <- "Piano"
}
}

# Assign Skill Change
for (i in change_1){
dt_vel_diff$Subcomponent[dt_vel_diff$Skill == "articulation" & dt_vel_diff$Interval == i] <- "LtoS"
dt_vel_diff$Subcomponent[dt_vel_diff$Skill == "dynamics" & dt_vel_diff$Interval == i] <- "FtoP"
}
for (i in change_2){
dt_vel_diff$Subcomponent[dt_vel_diff$Skill == "articulation" & dt_vel_diff$Interval == i] <- "StoL"
dt_vel_diff$Subcomponent[dt_vel_diff$Skill == "dynamics" & dt_vel_diff$Interval == i] <- "PtoF"
}

>>>>

# packages
if (!require("data.table")) {install.packages("data.table"); require("data.table")}
if (!require("ggpubr")) {install.packages("ggpubr"); require("ggpubr")}

@@

# KV
```{r vel, include = FALSE}
dt_vel <- data_onset
dt_vel$Note <- rep(1:72, nrow(dt_vel)/72)

# assign Subcomponents
dt_vel$Subcomponent <- "NA"
# Legato
for (phrase in 1:length(ls_legato2)){
   for (note in 1:length(ls_legato2[[phrase]])){
     dt_vel[Skill == "articulation" & Note == ls_legato2[[phrase]][note]]$Subcomponent <- "Legato"
   }
}
# Staccato
for (phrase in 1:length(ls_staccato2)){
   for (note in 1:length(ls_staccato2[[phrase]])){
     dt_vel[Skill == "articulation" & Note == ls_staccato2[[phrase]][note]]$Subcomponent <- "Staccato"
   }
}

@@

# assign Subcomponents
dt_vel_diff$Subcomponent <- "NA"
# Legato
for (phrase in 1:length(ls_legato)){
for (note in 1:length(ls_legato[[phrase]])){
  dt_vel_diff[Skill == "articulation" & Interval == ls_legato[[phrase]][note]]$Subcomponent <- "Legato"
}
}
# Staccato
for (phrase in 1:length(ls_staccato)){
for (note in 1:length(ls_staccato[[phrase]])){
  dt_vel_diff[Skill == "articulation" & Interval == ls_staccato[[phrase]][note]]$Subcomponent <- "Staccato"
}
}

# Forte
for (phrase in 1:length(ls_forte)){
for (note in 1:length(ls_forte[[phrase]])){
  dt_vel_diff[Skill == "dynamics" & Interval == ls_forte[[phrase]][note]]$Subcomponent <- "Forte"
}
}
# Piano
for (phrase in 1:length(ls_piano)){
for (note in 1:length(ls_piano[[phrase]])){
  dt_vel_diff[Skill == "dynamics" & Interval == ls_piano[[phrase]][note]]$Subcomponent <- "Piano"
}
}

# assign Subcomponent Change
for (i in change_1){
dt_vel_diff[Skill == "articulation" & Interval == i]$Subcomponent <- "LtoS"
dt_vel_diff[Skill == "dynamics" & Interval == i]$Subcomponent <- "FtoP"
}
for (i in change_2){
dt_vel_diff[Skill == "articulation" & Interval == i]$Subcomponent <- "StoL"
dt_vel_diff[Skill == "dynamics" & Interval == i]$Subcomponent <- "PtoF"
}
